Parsing Postfix log files

### 2009-04-02 doc/logparser-implementation.tex
Updated results after stats-max run finished. Added perfect best and perfect worst graph, and a table showing the std dev etc. Worked on graph and table placement, without much success.  I think manual     tweaking will be required, though adding 'h' back into the placement list     has helped. Added a graph for the number of times each action is invoked.

\newlength{\belowcaptionskipORIG}
\setlength{\belowcaptionskipORIG}{\belowcaptionskip}
\setlength{\belowcaptionskip}{10pt}
\showgraph{database-schema}{Diagram of the Database Schema}{Diagram
of the Database Schema picture}
\setlength{\belowcaptionskip}{\belowcaptionskipORIG}

@@

Actions are the component of this architecture responsible for processing
all of the inputs recognised by rules; in \parsername{} they reconstruct
the journey each mail takes through Postfix, dealing with all the
complications and difficulties that arise.  \parsername{} has
\numberOFactions{} actions and \numberOFrules{} rules, with an uneven
distribution of rules to actions as shown in \graphref{Distribution of
rules per action}.  Unsurprisingly, the action with the most associated
rules is \action{DELIVERY\_REJECTED}, the action that processes Postfix
rejecting a mail delivery attempt.  The next most common action is, perhaps
surprisingly, \action{UNINTERESTING}: this action does nothing when
invoked, allowing uninteresting log lines to be parsed without any effects
(it does not imply that the input is ungrammatical or unparsed).  Generally
rules specifying the \action{UNINTERESTING} action recognise log lines that
are not associated with a specific mail, e.g.\ notices about configuration
files changing; these log lines are recognised and processed so that the
framework can warn about unrecognised log lines, informing the user that
they need to add to or extend their ruleset.  Most of the remaining actions
have only one or two associated rules: some are specialised actions
required to address a deficiency in the log files, or a complication that
arises during parsing; other actions will only ever have one log line
variant, e.g.\ all log lines showing that a remote client has connected are
recognised by a single rule and handled by the \action{CONNECT} action.
\parsernames{} actions are described in detail in \sectionref{actions in
detail in implementation}, and \sectionref{adding new actions in
implementation} covers the process of adding a new action.

@@

>>>>

\newlength{\belowcaptionskipORIG}
\setlength{\belowcaptionskipORIG}{\belowcaptionskip}
\setlength{\belowcaptionskip}{10pt}
\showgraph{build/database-schema}{Diagram of the Database Schema}{Diagram
of the Database Schema picture}
\setlength{\belowcaptionskip}{\belowcaptionskipORIG}

@@

Actions are the component of this architecture responsible for processing
all of the inputs recognised by rules; in \parsername{} they reconstruct
the journey each mail takes through Postfix, dealing with all the
complications and difficulties that arise.  \parsername{} has
\numberOFactions{} actions and \numberOFrules{} rules, with an uneven
distribution of rules to actions as shown in \graphref{Distribution of
rules per action}.  Unsurprisingly, the action with the most associated
rules is \action{DELIVERY\_REJECTED}, the action that processes Postfix
rejecting a mail delivery attempt; next is \action{SAVE\_DATA}, the action
that saves useful information without doing any other processing.  The
third most common action is, perhaps surprisingly, \action{UNINTERESTING}:
this action does nothing when invoked, allowing uninteresting log lines to
be parsed without any effects (it does not imply that the input is
ungrammatical or unparsed).  Generally rules specifying the
\action{UNINTERESTING} action recognise log lines that are not associated
with a specific mail, e.g.\ notices about configuration files changing;
these log lines are recognised and processed so that the framework can warn
about unrecognised log lines, informing the user that they need to add to
or extend their ruleset.  Most of the remaining actions have only one or
two associated rules: some are specialised actions required to address a
deficiency in the log files, or a complication that arises during parsing;
other actions will only ever have one log line variant, e.g.\ all log lines
showing that a remote client has connected are recognised by a single rule
and handled by the \action{CONNECT} action.

XXX RUN test-some, STITCH THE COUNTS OF NUMBER OF RULES INVOKED INTO THE
REAL TIMING DATA, UPDATE THE NUMBER OF INVOCATIONS GRAPH, AND WRITE ABOUT
IT\@.

\parsernames{} actions are described in detail in \sectionref{actions in
detail in implementation}, and \sectionref{adding new actions in
implementation} covers the process of adding a new action.

@@

\showgraph{build/graph-number-of-action-invocations}{Number of times each
action was invoked when parsing \numberOFlogFILES{} log files}{Number of times
each action was invoked}

### 2009-04-02 doc/logparser-results.tex
Updated results after stats-max run finished. Added perfect best and perfect worst graph, and a table showing the std dev etc. Worked on graph and table placement, without much success.  I think manual     tweaking will be required, though adding 'h' back into the placement list     has helped. Added a graph for the number of times each action is invoked.

\clearpage{} % XXX GRAPHS MOVE AROUND A LOT
\subsection{Rule Ordering For Efficiency}

@@

\clearpage{} % XXX GRAPHS MOVE AROUND DURING REBUILDS

@@

>>>>

\subsection{Rule Ordering For Efficiency}

@@

@@

XXX ADD A TABLE SHOWING PERFECT WORST RELATIVE TO PERFECT BEST\@.

\showgraph{build/graph-perfect-best-and-perfect-worst-and-optimal-and-reverse-vs-shuffled}{Parsing
time including perfect best and worst relative to shuffled
ordering}{Parsing time relative to shuffled ordering including perfect best
and worst graph}

\showtable{build/include-perfect-best-and-optimal-and-reverse-and-perfect-worst-vs-shuffle}{Parsing
time including perfect best and worst relative to shuffled
ordering}{Parsing time including perfect best and worst relative to
shuffled ordering table}

% XXX \FloatBarrier{} MIGHT BE USEFUL TO CONTROL WHERE FLOATS ARE PLACED.
